% to compile this document use the following four commands: 
% pdflatex worms.tex
% bibtex worms.aux
% pdflatex worms.tex
% pdflatex worms.tex
\documentclass[12pt]{scrartcl}

% used packages
\usepackage{graphicx}
\usepackage{url}
\usepackage{listings}

% settings for listings
\lstset{language=Java}
\lstset{frame=single}
\lstset{framesep=10pt}
\lstset{basicstyle=\ttfamily}

% title, authors and date
\title{Oblig 2 \\ Creating a Domain Specific Language using the Eclipse Modelling Framework}
\author{Tobias Birmili, Florian Hagenauer, Kacper Surdy}

\date{07.05.2012}

\begin{document}

\maketitle

\tableofcontents

\section{Introduction}

This article is part of the second assignment for the course Modelbased System Development. The article discusses
how the three parts of the assignment have been solved. The basic task was to build a model for customer journeys,
make it possible to extract statistics out of customer journeys and finally the option to choose between three
additional tasks. It was possible to chose between a user-friendly editor, a graphical exporter or adding support
for multiple journeys. For this article the graphical export option was chosen.

Section \ref{section:model} describes how the model was built and discusses the different components. The second
section \ref{section:statistic} depicts which statistics were generated and finally Section \ref{section:export}
shows a solution for a graphical exporter which generates useful graphs.

\section{Creating a DSL metamodel with EMF} \label{section:model}

The first part of the work was to create a metamodel using the Eclipse Modelling Framework (EMF) for a customer
journey.
\section{Making a transformation to extract statistics} \label{section:statistic}

\section{Graphical Export} \label{section:export}


\end{document}